FinalManuscript_DISCS_UG

### 2018-10-06 parts/02_relatedliterature_05partiallyhomomorphic.tex
Random fixes

\subsubsection{Homomorphic Properties of the Pailler Cryptosystem}
The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message. These operations are defined as follows.
For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
\begin{align*}
  D(E(m_1)g^k\bmod n^2)=(m_1+k)\bmod n & \text{ (used to add a constant)}\\
  D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used for binary addition)}
  D(E(m_1)^k\bmod n^2)= km_1\bmod n & \text{ (used to multiply a plaintext constant)}
\end{align*}

@@

\subsubsection{Homomorphic Properties of the DGK Cryptosystem}
The DGK cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message. These operations are defined as follows.
For all $m_1,m_2 \in \mathbb{Z}_u$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
\begin{align*}
    D(E(m_1)g^k)=(m_1+k)\bmod u & \text{ (used to add a constant)}\\
    D(E(m_1)E(m_2))=(m_1+m_2)\bmod u & \text{ (used for binary addition)}
    D(E(m_1)^k)= km_1\bmod u & \text{ (used to multiply a plaintext constant)}
\end{align*}

>>>>

\subsubsection{Homomorphic Properties of the Pailler Cryptosystem}
The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message. These operations are defined as follows.
For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
\begin{align*}
  D(E(m_1)g^k\bmod n^2)=(m_1+k)\bmod n & \text{ (used to add a constant)}\\
  D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used for binary addition)}\\
  D(E(m_1)^k\bmod n^2)= km_1\bmod n & \text{ (used to multiply a plaintext constant)}
\end{align*}

@@

\subsubsection{Homomorphic Properties of the DGK Cryptosystem}
The DGK cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message. These operations are defined as follows.
For all $m_1,m_2 \in \mathbb{Z}_u$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
\begin{align*}
    D(E(m_1)g^k)=(m_1+k)\bmod u & \text{ (used to add a constant)}\\
    D(E(m_1)E(m_2))=(m_1+m_2)\bmod u & \text{ (used for binary addition)}\\
    D(E(m_1)^k)= km_1\bmod u & \text{ (used to multiply a plaintext constant)}
\end{align*}

### 2018-10-06 parts/08_appendices_a_cryptosystems.tex
Random fixes

%\section{Sample Questions for Different Studies}
%The following table presents three sample studies, as well as the guide questions that may help direct the discussion in each section of the paper. You may use this as another reference in writing your paper.
\chapter{CORRECTION TO THE DASGUPTA-PAL CRYPTOSYSTEM}
\label{ch:correction}
\section{Bitwise Description of the Dasgupta-Pal Cryptosystem}
The Dasgupta-Pal cryptosystem \cite{dasgupta_design_2016} encrypts each bit in a bit string independently.
In terms of the encryption of a single bit, the Dasgupta-Pal cryptosystem can be described as follows:
\begin{description}
	\item[Key generation]
	Let the secret key, $S_k$ be a large prime.
	Let the public refresh key, $R_k$, be $S_k \times z$, where $z$ is a large even integer.
	\item[Encryption]
	Given a message $m$, the encryption function is defined as
	\begin{align*}
		E(m) = m + S_kr
	\end{align*}
	where $r$ is a random integer.
	\item[Decryption]
	Given a ciphertext $c$, the decryption function is defined as
	\begin{align*}
		D(c) = c \bmod S_k \bmod 2
	\end{align*}
\end{description}
The homomorphic operations are then defined as
\begin{description}
	\item[XOR on ciphertexts]
	\begin{align*}
		D(E(a)+E(b)) = a \text{ XOR } b = (a + b) \bmod 2
	\end{align*}
	\item[AND on ciphertexts]
	\begin{align*}
		D(E(a)\times E(b)) = a \text{ AND } b = ab \bmod 2
	\end{align*}
\end{description}
After repeated operations on ciphertexts, the resulting ciphertext can grow in magnitude.
To prevent storage issues and keep the ciphertext size small, a refresh function is used.
\begin{description}
	\item[Refresh function]
	Given a ciphertext $c$, the refresh function is defined as
	\begin{align*}
		R(c) = c \bmod R_k
	\end{align*}
\end{description}
\section{Cases Where Decryption Fails}
We consider the following quantity:
\begin{align}
	\label{eq:cornercase_ciphertext}
	D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}}).
\end{align}
Since $S_k$ is odd, the corresponding operation in the plaintext space is
\begin{align*}
	\label{eq:cornercase_plaintext}
	\underbrace{1 \text{ XOR } 1 \text{ XOR } \cdots \text{ XOR } 1}_{S_k \text{ times}} = 1.
\end{align*}
However, evaluating Equation \ref{eq:cornercase_ciphertext} yields:
\begin{align*}
	D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}})
	&= D\left(\sum_{i=1}^{S_k}{(1+S_kr_i)}\right)\\
	&= D\left(S_k + S_k\sum_{i=1}^{S_k}{r_i}\right)\\
	&= \left(S_k + S_k\sum_{i=1}^{S_k}{r_i}\right) \bmod S_k \bmod 2\\
	&= 0 \bmod 2\\
	&= 0.
\end{align*}
Since $\underbrace{1 \text{ XOR } 1 \text{ XOR } \cdots \text{ XOR } 1}_{S_k \text{ times}} = 1\neq 0 = D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}})$, we have shown an instance where incorrect decryption occurs given a sequence of operations on ciphertexts.

\subsection{Proposed Correction and Proof of Correctness}
We now show that setting the secret key $S_k$ to $2p$, where $p$ is a prime, fixes the issue in the original cryptosystem.
\begin{theorem}
	Suppose $S_k = 2p$, where $p$ is a prime. Then when addition or multiplication is performed between any two ciphertexts, correct decryption is assured.
\end{theorem}
\begin{proof}
	Suppose $c_1, c_2$ are two ciphertexts such that
	\begin{align*}
		c_1 = a + S_kr_1\\
		c_2 = b + S_kr_2
	\end{align*}
	We first consider addition. We want to show that $(c_1+c_2)\bmod S_k$ has the same parity as $a+b$.
	By the division algorithm, we have $a+b = S_kq + r$, for some $q,r$, $q \geq 0, r > 0$. We can rewrite $c_1+c_2$ as
	\begin{align*}
		c_1+c_2 &= (a + S_kr_1) + (b + S_kr_2)\\
		&= (a+b)+ S_k(r_1 + r_2)\\
		&= (S_kq + r) + S_k(r_1 + r_2)\\
		&= r + S_k(q + r_1 + r_2).
	\end{align*}
	Therefore $(c_1+c_2)\bmod S_k = r$.
	It is enough to show that the parity of $a+b$ is the same as the parity of $r$. We consider cases based on the parity of $a+b$.
	\begin{description}
		\item[Case 1: $a+b$ is odd.]
			Since $a+b = S_kq + r$, $S_kq + r$ must also be odd.
			$S_k$ is even, so $S_kq$ is also even.
			For $S_kq + r$ to be odd, $r$ must be odd, since $S_k$ is even.

>>>>

%\section{Sample Questions for Different Studies}
%The following table presents three sample studies, as well as the guide questions that may help direct the discussion in each section of the paper. You may use this as another reference in writing your paper.
\chapter{CORRECTION FOR DASGUPTA-PAL}
\label{ch:correction}
\section{Bitwise Description of the Dasgupta-Pal Cryptosystem}
The Dasgupta-Pal cryptosystem \cite{dasgupta_design_2016} encrypts each bit in a bit string independently.
In terms of the encryption of a single bit, the Dasgupta-Pal cryptosystem can be described as follows:
\begin{description}
	\item[Key generation]
	Let the secret key, $S_k$ be a large prime.
	Let the public refresh key, $R_k$, be $S_k \times z$, where $z$ is a large even integer.
	\item[Encryption]
	Given a message $m$, the encryption function is defined as
	\begin{align*}
		E(m) = m + S_kr
	\end{align*}
	where $r$ is a random integer.
	\item[Decryption]
	Given a ciphertext $c$, the decryption function is defined as
	\begin{align*}
		D(c) = c \bmod S_k \bmod 2
	\end{align*}
\end{description}
The homomorphic operations are then defined as
\begin{description}
	\item[XOR on ciphertexts]
	\begin{align*}
		D(E(a)+E(b)) = a \text{ XOR } b = (a + b) \bmod 2
	\end{align*}
	\item[AND on ciphertexts]
	\begin{align*}
		D(E(a)\times E(b)) = a \text{ AND } b = ab \bmod 2
	\end{align*}
\end{description}
After repeated operations on ciphertexts, the resulting ciphertext can grow in magnitude.
To prevent storage issues and keep the ciphertext size small, a refresh function is used.
\begin{description}
	\item[Refresh function]
	Given a ciphertext $c$, the refresh function is defined as
	\begin{align*}
		R(c) = c \bmod R_k
	\end{align*}
\end{description}
\section{Cases Where Decryption Fails}
We consider the following quantity:
\begin{align}
	\label{eq:cornercase_ciphertext}
	D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}}).
\end{align}
Since $S_k$ is odd, the corresponding operation in the plaintext space is
\begin{align*}
	\label{eq:cornercase_plaintext}
	\underbrace{1 \text{ XOR } 1 \text{ XOR } \cdots \text{ XOR } 1}_{S_k \text{ times}} = 1.
\end{align*}
However, evaluating Equation \ref{eq:cornercase_ciphertext} yields:
\begin{align*}
	D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}})
	&= D\left(\sum_{i=1}^{S_k}{(1+S_kr_i)}\right)\\
	&= D\left(S_k + S_k\sum_{i=1}^{S_k}{r_i}\right)\\
	&= \left(S_k + S_k\sum_{i=1}^{S_k}{r_i}\right) \bmod S_k \bmod 2\\
	&= 0 \bmod 2\\
	&= 0.
\end{align*}
Since $\underbrace{1 \text{ XOR } 1 \text{ XOR } \cdots \text{ XOR } 1}_{S_k \text{ times}} = 1\neq 0 = D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}})$, we have shown an instance where incorrect decryption occurs given a sequence of operations on ciphertexts.

\section{Proposed Correction and Proof of Correctness}
We now show that setting the secret key $S_k$ to $2p$, where $p$ is a prime, fixes the issue in the original cryptosystem.
\begin{theorem}
	Suppose $S_k = 2p$, where $p$ is a prime. Then when addition or multiplication is performed between any two ciphertexts, correct decryption is assured.
\end{theorem}
\begin{proof}
	Suppose $c_1, c_2$ are two ciphertexts such that
	\begin{align*}
		c_1 = a + S_kr_1\\
		c_2 = b + S_kr_2
	\end{align*}
	We first consider addition. We want to show that $(c_1+c_2)\bmod S_k$ has the same parity as $a+b$.
	By the division algorithm, we have $a+b = S_kq + r$, for some $q,r$, $q \geq 0, r > 0$. We can rewrite $c_1+c_2$ as
	\begin{align*}
		c_1+c_2 &= (a + S_kr_1) + (b + S_kr_2)\\
		&= (a+b)+ S_k(r_1 + r_2)\\
		&= (S_kq + r) + S_k(r_1 + r_2)\\
		&= r + S_k(q + r_1 + r_2).
	\end{align*}
	Therefore $(c_1+c_2)\bmod S_k = r$.
	It is enough to show that the parity of $a+b$ is the same as the parity of $r$. We consider cases based on the parity of $a+b$.
	\begin{description}
		\item[Case 1: $a+b$ is odd.]
			Since $a+b = S_kq + r$, $S_kq + r$ must also be odd.
			$S_k$ is even, so $S_kq$ is also even.
			For $S_kq + r$ to be odd, $r$ must be odd, since $S_k$ is even.
